Creative Destruction in the Philosophy of Technology

### 2016-05-05 encryption/paper.tex
asdf

\usepackage{csquotes}
\usepackage{color}
\usepackage{amsfonts}

@@

\begin{document}
\maketitle

@@

>>>>

\usepackage{csquotes}
\usepackage{color}
\usepackage{amsfonts}
\usepackage{setspace}

@@

\begin{document}
\doublespacing

\maketitle

@@

\section{Parallel Situations}
To think about whether encryption is a fundamental right, it helps to think about parallel situations to communicated via encryption.
Encryption, as I will be thinking about it, is a method that allows two or more parties to send messages over the internet without an eavesdropper from reading, or learning any information about, the contents of the messages.
Encryption is also used to obfuscate data on a laptop or iPhone, such as in the recent case between the FBI and Apple, but I believe that it will simplify our reasoning if we leave that situation to another day.

One way to think about encryption is verbally talking to another party in a private room, in which case we ask the question: if we are alone in a private room with another party, do we have the right to communicate privately - that is, do we have a right to \textit{not} be eavesdropped on?
The legal answer to this question turns out, somewhat unsuprisingly, to be complex and situatational.
The law varies based on the state, but if you are talking in a business setting and the organization hosting the conversation makes a reasonable effort to inform the parties that they are being audio-visually recorded, then it is legal.
% https://www.quora.com/Is-it-legal-to-bug-a-workplace-conference-room-in-the-US
Let us ignore the case of a business, and consider a private residence: it is my lay understanding that homes can only be audio-visually surveilled if the law-enforcement body acquires a warrant, and it is illegal for a private-party to audio-visually surveil a private residence.
